Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-06 prop_letter.tex
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Updating...

Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
the space of events includes only mutually commuting sub-events, where
$\events'\subseteq\events$ is called a sub-event space if it satisfies
the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents experimenter know nothing about a coin before she tosses
it. Moreover, for each $p\in\left[0,1\right]$, the mixed state~$p\proj{0}+\left(1-p\right)\proj{1}$
represents a classical coin with probability~$p$ to get head, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$
on $\events_{0}$ because any classical coin should be consistent
with the situation where an experimenter has no prior knowledge.

In general, measurements done with limited resources and poor precision
may not uniquely identify the true state of a classical system. When
the system satisfies an extra-condition called convex, there is always
at least one system that is consistent with the measurements.

>>>>

Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
the space of events includes only mutually commuting sub-events, where
$\events'\subseteq\events$ is called a sub-event space if it satisfies
the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability~$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

In general, measurements done with limited resources and poor precision
may not uniquely identify the true state of a classical system. However,
at least one system is consistent with the measurements when the system
satisfies an extra-condition called convex.
